\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
more

\todo{(Discussion of expanding this work to terrestrial planets and/or reflected light:)} \citep{Berdyugina2017,Cowan2009,Cowan2018,Haggard2018,Kawahara2010,Fujii2012,Lustig-Yaeger2018} and others.

The \TESS mission promises to deliver thousands of new exoplanets around bright, 
nearby stars, many of which may be terrestrial worlds potentially suitable for life. 
In fact, one such world, a planet which we will call Sol d, has already been 
extensively observed by \TESS.

@@

We downloaded 
\footnote{\url{https://archive.stsci.edu/missions/tess/models/}}
the Solar System and \TESS ephemeris data for
Sectors 1 and 2 and used \spiceypy \citep{Acton1996, Acton2017, Annex2017}
to convert the TJD timestamps to 
ephemeris time (ET). We then used the \textsf{spkezr} utility of \spiceypy to compute
the relative positions of Sol, Sol d, and \TESS for every cadence
in our dataset in the J2000 equatorial reference frame. In this right-handed
coordinate frame, Sol d is centered at the origin, the $y$ axis points along the 
planet's spin axis, and the $x$ axis points toward the vernal equinox. We
do not apply any light travel correction, as the expected delay is on the order
of a few seconds.

>>>>

However, obtaining a map of a temperate terrestrial exoplanet is still
beyond the capabilities of current facilities, as both the thermal and 
reflected light signals from these planets
are orders of magnitude below current measurement capabilities. Nevertheless,
much work has been done on the theoretical front on mapping terrestrial
planets in the habitable zone
\citep[e.g.,][]{Kawahara2010,Fujii2012,Berdyugina2017,Haggard2018,Lustig-Yaeger2018};
for a review, see \cite{Cowan2018}.

In this work, we show how we can harness photometric data collected by the \TESS mission
to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$ m
orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
star. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
the habitable zone for follow-up with other missions, it came as a great surprise
to us that data from the spacecraft could be used not only to detect Sol d but to
characterize it in detal. This is due primarily to the strong nature of the reflected
light signal originating from the planet, which 
due to complex internal optics illuminates the entirety of the \TESS detector 
during most of Sector 1 and part of Sector 2.

\todo{more}

@@

We downloaded%
\footnote{\url{https://archive.stsci.edu/missions/tess/models/}}
the Solar System and \TESS ephemeris data for
Sectors 1 and 2 and used \spiceypy \citep{Acton1996, Acton2017, Annex2017}
to convert the TJD timestamps to 
ephemeris time (ET). We then used the \textsf{spkezr} utility of \spiceypy to compute
the relative positions of Sol, Sol d, and \TESS for every cadence
in our dataset in the J2000 equatorial reference frame. In this right-handed
coordinate frame, Sol d is centered at the origin, the $y$ axis points along the 
planet's spin axis, and the $x$ axis points toward the vernal equinox. We
do not apply any light travel correction, as the expected delay is on the order
of a few seconds.
